Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-27 cvx-flats-neurips21/cvx-flats.tex
finished section 4?

\tikzstyle{cell}=[dashed,thick]
\tikzstyle{simplex}=[thick]
\newcommand{\tikzfigscale}{2.2}
\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.7) {#1};}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

@@

\newcommand{\ellbar}{\underline{\ell}}
\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
\newcommand{\iden}{\mathrm{iden}}
\newcommand{\im}{\mathrm{im}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\CVaR}{\mathrm{CVaR}}
\newcommand{\mode}{\Gamma_{\mathrm{mode}}}

@@

\jessiet{Do we still want this following paragraph?}
\raft{Good question.  I edited a bit, but still up for discussion.}
%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
Therefore, property elicitation -- which studies the relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}  -- allows us to study general lower bounds that apply across all four quadrants.
%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.

@@

Implicit in the above elicitation definitions is that $L\in\L$, meaning $L$ is minimizable: since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, the expected loss $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in previous work, e.g.,~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.\bo{I think this is too much here. It could go in a discussion section but it bogs this down.}
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
\bo{It's not clear exactly why we mention this.} \jessie{It feels so related but good point that it's not.  I think at one point we talked about relationships to embedding dimension in future work.  Do we want to flesh out the concept of ``prediction dimension'' and the hierarchy of prediction dimension $\geq$ ccdim $=$ convex consistency dim $\geq$ convex elicitation complexity $\geq$ embedding dimension?  It's a little tricky to illustrate because of the quadrants... Also feels like an aside, but related to my comment in the abstract.}
%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

@@

\paragraph{Q2: Variation of hierarchical classification.}
\jessiet{I don't like this phrasing, since it seems like we're pointing to Q1 then swerve to Q2}
\raft{Good point; reworded}
\citet{ramaswamy2015hierarchical} study hierarchical classification tasks, in which labels are arranged in a tree and one wishes to predict the deepest node in a tree that is ``likely enough'' \citep{xiao2007hierarchical,burkhardt2005database}.
Consider the variation of this task where one can only predict leaves of this tree.
For example, Figure~\ref{fig:hierarchical-tree} depicts a speech classification task where speech is either active or non-active, and non-active is further subdivided into median and passive.
It is natural to predict active if that label is more likely than both non-active labels combined, and otherwise to predict the most likely of median and passive:
\begin{align*}
\gamma(p) &= \begin{cases}
\text{active} & p_{\text{active}} \geq 1/2 \\
\text{median} & p_{\text{active}} \leq 1/2 \wedge p_{\text{median}} \geq p_{\text{passive}} \\
\text{passive} & p_{\text{active}} \leq 1/2 \wedge p_{\text{passive}} \geq p_{\text{median}} \\
\end{cases}~.
\end{align*} 
This ``T-shaped'' property is depicted in Figure~\ref{fig:quadrants-simplices} (Q2).
This task falls under Quadrant 2, as this property is not elicited by any target loss.%
\footnote{The cells of every finite elicitable property form a power diagram, which disallow this ``T-shaped'' configuration~\cite{lambert2009eliciting,frongillo2014general}.}
Like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through the depicted $p$, so 
%Theorem~\ref{thm:convex-flats-inf-dim} 
Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} gives $\conscvx(\gamma) = 2$.

\begin{SCfigure}
	\centering
	\begin{tikzpicture}
\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=4pt, fill = white];
\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=4pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
\tikzstyle{every node}=[font=\small];

@@

\paragraph{Q4: Variance}
Consider the task of estimating the variance $\Gamma^\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
Interestingly, the variance is not elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
In \S~\ref{app:omitted-examples}, we show $\eliccvx(\Gamma^\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in \S~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss. % $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.

@@

        \begin{scope}
          \clip (h) -- (m) -- (l) -- (h);
          \foreach \c in {0,0.1,...,1}
          {
            \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
            \pgfmathsetmacro\bb{0.5*\c}
            \coordinate (A) at ($(\aa,1-\aa,0)$);
            \coordinate (B) at ($(1-\aa,\aa,0)$);
            \coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
            \draw[myblue,thin] (C) parabola (A);
            \draw[myblue,thin] (C) parabola (B);
          }
          \def\c{0.6}
          \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
          \pgfmathsetmacro\bb{0.5*\c}
          \coordinate (A) at ($(\aa,1-\aa,0)$);
          \coordinate (B) at ($(1-\aa,\aa,0)$);
          \coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
          \coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
          \coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
          \coordinate (centerdot) at (0.21,0.445, 0.345);
          \draw[myblue, very thick] (C) parabola (A);
          \draw[myblue, very thick] (C) parabola (B);
          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
          \node at (centerdot) {$\bullet$};
        \end{scope}
        \def\c{0.6}
        \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
        \pgfmathsetmacro\bb{0.5*\c}
        \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {\vphantom{$\Gamma_{0.1}$}};
        \node (levset) at (0.5,0.5,-.15) {$\Gamma_{0.6}$};
        \draw[-latex,thin] (levset) edge[in=330,out=180] ($(\aa,1-\aa,0)$);
        \draw[-latex,thin] (levset) edge[in=210,out=0] ($(1-\aa,\aa,0)$);
        \placefiglabel{(Q4)}
      \end{tikzpicture}
      \hspace*{-10pt}
      % \\
      % \hline
  \end{tabular}
\caption{Example properties for each quadrant. 
Throughout, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
(Q1,Q2) We cannot fit a $1$-flat (line) through $p$ without leaving the level sets $\gamma_\bot$ and $\gamma_{\text{median}}$, respectively;
Theorem~\ref{thm:convex-flats-inf-dim} implies that there is no $1$-dimensional consistent convex surrogate for either problem.
(Q3) Squared error is a $1$-dimensional convex loss, and indeed it elicits the mean of $Y$, whose level sets are all $1$-flats.
(Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.
-}\label{fig:quadrants-simplices}
\end{SCfigure}

@@

Using our $d$-flats framework, we establish such bounds, thus resolving both open questions.
The central observation is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are \emph{unions} of $d$-flats from Theorem~\ref{thm:convex-flats-inf-dim}.
It turns out that the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} essentially rely only on the containment of $d$-flats in other level sets, rather than the full structure of identifiable properties.
As such, although quite subtle in the case of risk measures, we can modify their arguments for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher in some cases.

@@

The problem of estimating a risk or uncertainty measure of $Y$ has applications in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review}, robust engineering design\raft{add cites from AFOSR or EnvAI}, and algorithmic fairness~\citep{williamson2019fairness}.
For examples of risk measures, one may wish to estimate the upper confidence bound $\E[Y] + \lambda \Var[Y]$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
Uncertainty measures can be unbiased versions, such as the variance, or an entropy or norm of the distribution of $Y$.
Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.

We resolve this open question using our $d$-flats framework, giving a matching result (Theorem~\ref{thm:bayes-risk-lower-bound}) for convex-elicitable properties.
% \citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
% With a careful modification of their argument, we can extend this observation to unions of $d$-flats.
First we recall the definition of the Bayes risk.

@@

\begin{theorem}\label{thm:mode}
  The mode has $\conscvx(\mode) = \eliccvx(\mode) = \infty$ (countably infinite) with respect to $\P$, the class of probability measures on $\Y=\reals$ which admit a smooth and bounded density and such that $\mode$ is single-valued.
\end{theorem}
\begin{proof}
  The proof of \citet[Theorem 1]{dearborn2020indirect} gives a distribution $p\in\P$ with $\mode(p) = 0 =: u$.
  It then introduces an arbitrary identification function $V:\hat\R\times\Y\to\reals^k$, $k\in\mathbb{N}$, and value $r\in\hat\R$ such that $p \in \zeros{V(r,\cdot)}$.
  Letting $F = \zeros{V(r,\cdot)}$, we therefore have an arbitrary $k$-flat containing $p$.
  The proof then proceeds to construct some $p'\in F$ with $\mode(p') \neq u$.
  Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} now gives $\conscvx(\mode) \geq \eliccvx(\mode) \geq k+1$.
  \raft{PROBLEM: the set $\P$ is not convex.  Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.  Do we really need $\P$ to be convex for Theorem~\ref{thm:convex-flats-inf-dim}?}
  As $k$ was arbitrary, the result follows.
\end{proof}

A closely related property for any $\beta > 0$ is the (midpoint of the) modal interval of width $2\beta$, given by $\Gamma_\beta(p) = \argmax_{x\in\reals} p([x-\beta,x+\beta])$.
Interestingly, unlike the mode for $\Y=\reals$, the modal interval is elicitable, by the target loss $\ell_\beta(r,y) = \ones\{|r-y| > \beta\}$.
The problem of estimating the modal interval therefore could be thought of as falling under Quadrant 3.

As observed in \citet[Corollary 1]{dearborn2020indirect}, the properties $\mode$ and $\Gamma_\beta$ coincide with the family of distributions needed in their Theorem 1, meaning the conclusion of Theorem~\ref{thm:mode} transfers to the modal interval as well.
\begin{corollary}\label{cor:modal-interval}
  For any $\beta > 0$, the modal midpoint, $\Gamma_\beta: \P_\beta \to \reals$, has  $\conscvx(\Gamma_\beta) = \eliccvx(\Gamma_\beta) = \infty$ (countably infinite) with respect to $\P_\beta$, the class of unimodal probability measures on $\Y=\reals$ which admit a smooth and bounded density, and such that $\mode$ and $\Gamma_\beta$ are single-valued.
\end{corollary}

Thus, while $\Gamma_\beta$ is elicitable, it does not have any consistent finite-dimensional convex surrogate.
\raf{Discussion of why this sort of makes sense as a limit of 0-1 loss and the mode.}

>>>>

\tikzstyle{cell}=[dashed,thick]
\tikzstyle{simplex}=[thick]
\newcommand{\tikzfigscale}{2.2}
\newcommand{\placefiglabel}[1]{\node at (1.1,0,1.5) {#1};}
\usetikzlibrary{arrows}
\usetikzlibrary{shapes}

@@

\newcommand{\ellbar}{\underline{\ell}}
\newcommand{\lbar}{\underline{L}} % couldn't do L* while proofreading...
\newcommand{\iden}{\mathrm{iden}}
\newcommand{\im}{\mathrm{im}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\CVaR}{\mathrm{CVaR}}
\newcommand{\mode}{\gamma_{\mathrm{mode}}}
\newcommand{\modal}{\gamma_\beta}

@@

\jessiet{Do we still want this following paragraph?}
\raft{Good question.  I edited a bit, but still up for discussion.}
%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds that apply across all four quadrants.

% relationship between target losses, target statistics, surrogate losses, and surrogate statistics, see \S~\ref{subsec:properties}---
%Most prior work on convex consistency dimension focuses on problems in Quadrant 1~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,ramaswamy2015hierarchical,ramaswamy2016convex,ramaswamy2018consistent}.

@@

Implicit in the above elicitation definitions is that $L\in\L$, meaning $L$ is minimizable: since $\Gamma = \prop[\P]{L}$ is nonempty everywhere, the expected loss $\exploss{L}{\cdot}{p}$ always achieves a minimum.
This restriction is also implicit in previous work, e.g.,~\citep{agarwal2015consistent}.
While some popular surrogates such as logistic and exponential loss are not minimizable, these losses are still covered in Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} and Theorem~\ref{thm:bayes-risk-lower-bound} as $\Gamma(p) \neq \emptyset$ when $p\in\P := \relint\simplex$; moreover, by thresholding $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$ we can achieve $L'\in\L$ for both.
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray) would allow us to assume minimizability without loss of generality, as convex losses would always admit this more general minimizer.
\botodo{I think this is too much here. It could go in a discussion section but it bogs this down.}
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

@@

\citet[Corollary 10]{agarwal2015consistent} provide a necessary condition for the direct convex elicitation of single-valued properties, yielding bounds on the dimensionality of level sets.
Moreover, \citet{finocchiaro2019embedding} study surrogate losses which \emph{embed} a discrete loss, which is a special case of indirect elicitation.
%They construct calibrated link functions from embeddings, which together with observations about indirect elicitation, imply that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
\citet{finocchiaro2020embedding} further introduce the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex consistency dimension of discrete losses and finite statistics.
\botodo{It's not clear exactly why we mention this.} \jessiet{It feels so related but good point that it's not.  I think at one point we talked about relationships to embedding dimension in future work.  Do we want to flesh out the concept of ``prediction dimension'' and the hierarchy of prediction dimension $\geq$ ccdim $=$ convex consistency dim $\geq$ convex elicitation complexity $\geq$ embedding dimension?  It's a little tricky to illustrate because of the quadrants... Also feels like an aside, but related to my comment in the abstract.}
%Since embedding is a special case of indirect elicitation, we have the chain of inequalities, embedding dimension $\leq$  ``polyhedral calibration dimension'' $\leq$ convex calibration dimension; it is an open problem whether any of these inequalities can be strict.

@@

\paragraph{Q2: Variation of hierarchical classification.}
\citet{ramaswamy2015hierarchical} study hierarchical classification tasks, in which labels are arranged in a tree and one wishes to predict the deepest node in a tree that is ``likely enough'' \citep{xiao2007hierarchical,burkhardt2005database}.
Consider the variation of this task where one can only predict leaves of this tree.
For example, Figure~\ref{fig:hierarchical-tree} depicts a speech classification task where speech is either active or non-active, and non-active is further subdivided into median and passive.
It is natural to predict active if that label is more likely than both non-active labels combined, and otherwise to predict the most likely of median and passive:
\begin{align*}
\gamma(p) &= \begin{cases}
\text{active} & p_{\text{active}} \geq 1/2 \\
\text{median} & p_{\text{active}} \leq 1/2 \wedge p_{\text{median}} \geq p_{\text{passive}} \\
\text{passive} & p_{\text{active}} \leq 1/2 \wedge p_{\text{passive}} \geq p_{\text{median}} \\
\end{cases}~.
\end{align*} 
This ``T-shaped'' property is depicted in Figure~\ref{fig:quadrants-simplices} (Q2).
This task falls under Quadrant 2, as this property is not elicited by any target loss.%
\footnote{The cells of every finite elicitable property form a power diagram, which disallow this ``T-shaped'' configuration~\cite{lambert2009eliciting,frongillo2014general}.}
Like abstain, we cannot fit a $1$-flat (line) entirely contained in the level set $\gamma_{\text{passive}}$ through the depicted $p$, so 
%Theorem~\ref{thm:convex-flats-inf-dim} 
Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} gives $\conscvx(\gamma) = 2$.

\begin{SCfigure}
	\centering
	\begin{tikzpicture}[yscale=0.6]
\tikzstyle{vertex} = [draw, minimum width=4em, inner sep=2pt, fill = white];
\tikzstyle{vertexblue} = [draw, minimum width=4em, inner sep=2pt, fill = blue, fill opacity = 0.2, text=black, text opacity = 1.];
\tikzstyle{every node}=[font=\small];

@@

\paragraph{Q4: Variance}
Consider the task of estimating the variance $\Var(p) = \E_p[Y^2] - \E_p[Y]^2$.
Interestingly, the variance is not elicitable as its level sets are not convex~\cite{osband1985providing,lambert2008eliciting}, meaning this task falls under Quadrant 4.
The fact that the variance is not elicitable does not yield a lower bound on elicitation complexity of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.
In \S~\ref{app:omitted-examples}, we show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} in \S~\ref{sec:contin-consis} using the fact that variance is the Bayes risk of squared loss. % $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.

@@

        \begin{scope}
          \clip (h) -- (m) -- (l) -- (h);
          \foreach \c in {0,0.1,...,1}
          {
            \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
            \pgfmathsetmacro\bb{0.5*\c}
            \coordinate (A) at ($(\aa,1-\aa,0)$);
            \coordinate (B) at ($(1-\aa,\aa,0)$);
            \coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
            \draw[myblue,thin] (C) parabola (A);
            \draw[myblue,thin] (C) parabola (B);
          }
          \def\c{0.6}
          \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
          \pgfmathsetmacro\bb{0.5*\c}
          \coordinate (A) at ($(\aa,1-\aa,0)$);
          \coordinate (B) at ($(1-\aa,\aa,0)$);
          \coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
          \coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
          \coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
          \coordinate (centerdot) at (0.21,0.445, 0.345);
          \draw[myblue, very thick] (C) parabola (A);
          \draw[myblue, very thick] (C) parabola (B);
          \draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/10,9/10,0) -- (centerdot);
          \node at (centerdot) {$\bullet$};
        \end{scope}
        \def\c{0.6}
        \pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
        \pgfmathsetmacro\bb{0.5*\c}
        \node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {\vphantom{$\Gamma_{0.1}$}};
        \node (levset) at (0.5,0.5,-.15) {$\Gamma_{0.6}$};
        \draw[-latex,thin] (levset) edge[in=330,out=180] ($(\aa,1-\aa,0)$);
        \draw[-latex,thin] (levset) edge[in=210,out=0] ($(1-\aa,\aa,0)$);
        \placefiglabel{(Q4)}
      \end{tikzpicture}
      \hspace*{-10pt}
      % \\
      % \hline
  \end{tabular}
\caption{Example properties for each quadrant. 
Throughout, we take $\bullet$ to be the distribution $p = (0.3, 0.3, 0.4)$ according to the left, top, and right outcomes respectively. 
(Q1,Q2) We cannot fit a $1$-flat (line) through $p$ without leaving the level sets $\gamma_\bot$ and $\gamma_{\text{median}}$, respectively;
Theorem~\ref{thm:convex-flats-inf-dim} implies that there is no $1$-dimensional consistent convex surrogate for either problem.
(Q3) Squared error is a $1$-dimensional convex loss, and indeed it elicits the mean of $Y$, whose level sets are all $1$-flats.
(Q4) The level sets of the variance are curved and cannot fit a $1$-flat; from Theorem~\ref{thm:convex-flats-inf-dim} there is no $1$-dimensional convex surrogate consistent for the variance.}\label{fig:quadrants-simplices}
\end{SCfigure}

@@

Using our $d$-flats framework, we resolve both open questions with new lower bounds in both settings.
% The central observation is that the level sets of $d$-dimensional convex-elicitable properties, if not $d$-flats themselves, are
Our framework clarifies the relationship between $d$-identifiable properties and properties elicited by $d$-dimensional convex losses: the level sets of the former are $d$-flats by definition, while the level sets of the latter are \emph{unions} of $d$-flats by Theorem~\ref{thm:convex-flats-inf-dim}.
A careful examination of the arguments of~\citet{frongillo2020elicitation} and~\citet{dearborn2020indirect} reveals that they largely rely on the containment of $d$-flats in level sets, rather than the full structure of identifiable properties.
As such, although quite subtle in the case of risk measures, the general structure of these previous proofs go through for convex-elicitable properties: since no $d$-flat could be contained in a particular level set, no union of $d$-flats could be either.
Our lower bounds therefore match both of these papers, though we conjecture that the convex consistency dimension is strictly higher in some cases.

@@

The problem of estimating a risk or uncertainty measure of $Y$ is of central importance in financial regulation~\cite{acerbi2014back-testing,fissler2016expected,campbell2005review} and robust engineering design\raft{add cites from AFOSR or EnvAI}.
% , and algorithmic fairness~\citep{williamson2019fairness}
Risk measures include the upper confidence bound $\E[Y] + \lambda \sqrt{\Var[Y]}$, or the Conditional Value at Risk (CVaR) defined below, in either conditional or unconditional contexts.
Uncertainty measures include the variance, entropy, or norm of the distribution of $Y$.
Risk and uncertainty measures are typically not elicitable, so this problem falls under Quadrant 4.
\citet{frongillo2020elicitation} give prediction dimension lower bounds for a broad class of risk and uncertainty measures, namely Bayes risks.
As stated above, these bounds are with respect to identifiable properties, and bounds for convex surrogates are left as a major open question.

We resolve this open question using our $d$-flats framework, giving a matching result for convex-elicitable properties (Theorem~\ref{thm:bayes-risk-lower-bound}).
% \citet{frongillo2020elicitation} rely on finding a dimension $d$ such that the level sets of certain risk measures $\gamma$ have too much curvature to contain any $d$-flat.
% With a careful modification of their argument, we can extend this observation to unions of $d$-flats.
First we recall the definition of the Bayes risk.

@@

\begin{theorem}\label{thm:mode}
  The mode has $\conscvx(\mode) = \eliccvx(\mode) = \infty$ (countably infinite) with respect to $\P$, the class of probability measures on $\Y=\reals$ with a smooth and bounded density and such that $\mode$ is single-valued.
\end{theorem}
\begin{proof}
  The proof of \citet[Theorem 1]{dearborn2020indirect} gives a distribution $p\in\P$ with $\mode(p) = 0 =: u$.
  It then introduces an arbitrary identification function $V:\hat\R\times\Y\to\reals^k$, $k\in\mathbb{N}$, and value $r\in\hat\R$ such that $p \in \zeros{V(r,\cdot)}$.
  Letting $F = \zeros{V(r,\cdot)}$, we therefore have an arbitrary $k$-flat containing $p$.
  The proof then proceeds to construct some $p'\in F$ with $\mode(p') \neq u$.
  Corollary~\ref{cor:Pcodim-flat-elic-relint-prop} now gives $\conscvx(\mode) \geq \eliccvx(\mode) \geq k+1$.
  \raft{PROBLEM: the set $\P$ is not convex.  Take two univariance Gaussians centered at 0 and 1: they are each in $\P$ but their mixture is not.  Do we really need $\P$ to be convex for Theorem~\ref{thm:convex-flats-inf-dim}?}
  As $k$ was arbitrary, the result follows.
\end{proof}

A closely related property for any $\beta > 0$ is the (midpoint of the) modal interval of width $2\beta$, given by $\modal(p) = \argmax_{x\in\reals} p([x-\beta,x+\beta])$.
Interestingly, unlike the mode for $\Y=\reals$, the modal interval is elicitable, by the target loss $\ell_\beta(r,y) = \ones\{|r-y| > \beta\}$.
The problem of estimating the modal interval therefore could be thought of as falling under Quadrant 3.

As observed in \citet[Corollary 1]{dearborn2020indirect}, the properties $\mode$ and $\modal$ coincide with the family of distributions needed in their Theorem 1, meaning the conclusion of Theorem~\ref{thm:mode} transfers to the modal interval as well.
\begin{corollary}\label{cor:modal-interval}
  For any $\beta > 0$, the modal interval $\modal: \P_\beta \to \reals$ has  $\conscvx(\modal) = \eliccvx(\modal) = \infty$ (countably infinite) with respect to $\P_\beta$, the class probability measures on $\Y=\reals$ with a smooth and bounded density, and such that $\mode$ and $\modal$ are single-valued.
\end{corollary}

Thus, while $\modal$ is elicitable, it does not have any consistent finite-dimensional convex surrogate.
While this statement may seem counter-intuitive, recall that the mode for finite $|\Y|$ has $\conscvx(\mode)=|\Y|-1$.
Taking the limit as $|\Y|\to\infty$, one may therefore expect an infinite convex consistency dimension for both the mode and modal interval.
